---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- Use snippet 'render_markdown' for it -->

```{r,echo=FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/"
)
```

# yamlme

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/yamlme)](https://cran.r-project.org/package=yamlme)
[![Rdoc](http://www.rdocumentation.org/badges/version/yamlme)](http://www.rdocumentation.org/packages/yamlme)
<br>
[![Travis build status](https://travis-ci.com/kamapu/yamlme.svg?branch=master)](https://travis-ci.com/kamapu/yamlme)
[![Codecov test coverage](https://codecov.io/gh/kamapu/yamlme/branch/master/graph/badge.svg)](https://codecov.io/gh/kamapu/yamlme?branch=master)
[![R-CMD-check](https://github.com/kamapu/yamlme/workflows/R-CMD-check/badge.svg)](https://github.com/kamapu/yamlme/actions)
<br>
[![CRAN_downloads](http://cranlogs.r-pkg.org/badges/yamlme)](https://cran.r-project.org/package=yamlme)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/yamlme)](https://cran.r-project.org/package=yamlme)
<!-- badges: end -->

## Installing yamlme

For installing this package use `devtools`:

```{r eval=FALSE}
library(devtools)
install_github("kamapu/yamlme", build_vignettes = TRUE)
```

After installing the package have to be loaded in the current R-session.

```{r eval=FALSE}
library(yamlme)
```

## Create a document

This package aims to save documents with their respective settings (yaml-head)
in R-objects.

```{r}
my_document <- write_rmd(title = "Mi First Document", author = "My Name",
		output = "html_document", append = "# This is a comment in head",
		body = txt_body(
				"# Starting a working day",
				"",
				"At the beginning of every day I will do:",
				"",
				"- Say everyone \"Good morning!\"",
				"- Start the coffe mashine",
				"- Start the computer",
				"- Read mails"))
my_document
```

By this way it is possible to produce documents from plain R-code. This
document can be then rendered by the function `render_rmd()`.

```{r eval = FALSE}
render_rmd(input = my_document, output_file = "my_document")
```

For more details, take a look on the vignette.

```{r eval = FALSE}
vignette("yamlme-intro")
```

## Similar packages

Other R-packages with similar tasks are
[`yaml`](https://github.com/viking/r-yaml/) and
[`ymlthis`](https://github.com/r-lib/ymlthis), where the later is quite close
but uses a different approach defining separated functions for different
elements, while `yamlme` uses a single function, which is quite open, writing
the head in accordance to the argument provided in custom parameters.
In addition, yamlme does not have any dependency.
