---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- Use snippet 'render_markdown' for it -->

```{r,echo=FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/"
)
```

# yamlme

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/yamlme)](https://cran.r-project.org/package=yamlme)
[![DOI](https://zenodo.org/badge/297735831.svg)](https://zenodo.org/badge/latestdoi/297735831)
<br>
[![R-CMD-check](https://github.com/kamapu/yamlme/workflows/R-CMD-check/badge.svg)](https://github.com/kamapu/yamlme/actions)
[![Codecov test coverage](https://codecov.io/gh/kamapu/yamlme/branch/master/graph/badge.svg)](https://codecov.io/gh/kamapu/yamlme?branch=master)
<br>
[![CRAN_downloads](http://cranlogs.r-pkg.org/badges/yamlme)](https://cran.r-project.org/package=yamlme)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/yamlme)](https://cran.r-project.org/package=yamlme)
<!-- badges: end -->

## Installing yamlme

You can install the last release from CRAN


```{r eval=FALSE}
install.packages("yamlme", dependencies = TRUE)
```

or the current development version from GitHub, using the package `devtools`:

```{r eval=FALSE}
library(devtools)
install_github("kamapu/yamlme", build_vignettes = TRUE)
```

After installing the package have to be loaded in the current R-session.

```{r}
library(yamlme)
```

## Create a document

This package aims to save documents with their respective settings (yaml-head)
in R-objects.

```{r}
my_document <- list(
    title = "Mi First Document",
    author = "My Name",
    output = "html_document",
    body = txt_body(
        "# Starting a working day",
		"",
		"At the beginning of every day I will do:",
		"",
		"- Say everyone \"Good morning!\"",
		"- Start the coffe mashine",
		"- Start the computer",
		"- Read mails"))
my_document <- as(my_document, "rmd_doc")
my_document
```

By this way it is possible to produce documents from plain R-code. This
document can be then rendered by the function `render_rmd()`.

```{r eval = FALSE}
render_rmd(input = my_document)
browseURL("my_document.html")
```

For more details, take a look on the vignette.

```{r eval = FALSE}
vignette("yamlme-intro")
```

## Similar packages

The package [`ymlthis`](https://github.com/r-lib/ymlthis) is targeting the
same tasks but using a different approach for it.

The most important dependencies of `yamlme` are
[`yaml`](http://biostat.app.vumc.org/wiki/Main/YamlR) and
[`rmarkdown`](https://rmarkdown.rstudio.com/).
