---
title: Test for yaml function
author: Miguel Alvarez
output: pdf_document
---

# Introduction

The package [`yamlme`](https://github.com/kamapu/yamlme) is developed to
enhance automatic generation of reports and documents from different packages,
for instance reporting data sources by the package
[`vegtable`](https://github.com/kamapu/vegtable) or producing check-lists by
the package [`taxlist`](https://github.com/kamapu/taxlist).
These applications are at the moment tested in an experimental way, for instance
in the package [`vegtable2`](https://github.com/kamapu/vegtable2) (see
function `report_communities()`).

The function `write_yaml()` is at the moment implemented in an own package.
For details, a brief description will be retrieved by `?write_yaml`.

```{r results="hide", message=FALSE}
devtools::install_github("kamapu/yamlme")
library(yamlme)
```

# State of the Art

The idea behind this function is to create Rmd documents with conten by using
R-code.
For instance a PDF document by setting the different yaml items as arguments in
the function.

```{r}
Docu <- write_yaml(
		title="First Function Version",
		author="Miguel Alvarez",
		output="pdf_document")
cat(Docu)
```

The names of the yaml entries are provided by the user, except for the defined
arguments `append`, `body`, and `filename`, which I am assuming are not
required in Rmarkdown documents.

To produce a full document, we need to include a body part, an output file and
render it with rmarkdown.

```{r eval=FALSE}
Docu <- write_yaml(
		title="First Function Version",
		author="Miguel Alvarez",
		output="pdf_document",
		body="This is a first incursion in Rmarkdown.",
		filename="test_doc.Rmd")
render("test_doc.Rmd")
```

**THE IDEA** is to insert the entries by a combination of 1) character vectors
of length 1 (the previous examples), 2) character vectors longer than 1 and 3)
complex structures by lists.
At the moment only alternatives 1 and 2 are implemented, while the challenge
with more complex entries is to make the formatting in a recursive way and at
the same time detect the hierarchical rank (depth) to properly set indentation.


```{r eval=FALSE}
Docu <- write_yaml(
		title="First Function Version",
		author="Miguel Alvarez",
		output="pdf_document",
		"header-includes"=c(
				"- \\usepackage[utf8]{inputenc}",
				"- \\usepackage[T1]{fontenc}"),
		append="# Document written with 'write_yaml()'",
		body="This is a first incursion in Rmarkdown.",
		filename="test_doc.Rmd")
```

Note that the name of the entry **header-includes** have to be quoted because
of the dash, while back-slashes have to be escaped.

# Desiderata

The next step should be to implement lists as arguments for hierarchical entries
in the yaml head.
For instance

```{r eval=FALSE}
output=list(
		pdf_file="default")
```

should write

```
---
output:
  pdf_document: default
---
```

A more complex example can be provided, for instance, by multiple outputs

```
---
output:
  html_document:
    toc: true
    toc_float: true
  word_document:
    fig_caption: false
---
```

In that case, the argument output should be

```{r eval=FALSE}
output=list(
		html_document=list(
				toc="true",
				toc_float="true"),
		word_document=list(
				fig_caption="false"))
```

The function is expected to generate automatically the structure of the head
entry depending on the structure of the list in the function.
The good news is that we can tweak the (current) limitations of `write_yaml()`
by using the argument `append`.

```{r eval=FALSE}
Docu <- write_yaml(
		title="First Function Version",
		author="Miguel Alvarez",
		append=paste(c(
						"# Appended code",
						"output:",
						"  html_document:",
						"    toc: true",
						"    toc_float: true",
						"  word_document:",
						"    fig_caption: false"),
				collapse="\n"),
		body=paste(c(
						"# Breakfast",
						"",
						"Just a cup of coffee.",
						"",
						"# Midday",
						"",
						"- A pizza from the Botan Grill",
						"- A bottle of coca-cola"),
				collapse="\n"),
		filename="test_doc.Rmd")
render("test_doc.Rmd", output_format="all")
```






