---
title: "Setting elements in yaml headers for r-markdown documents"
author: Miguel Alvarez
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting elements in yaml headers for r-markdown documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The package `yamlme` targets to write yaml-heads and even full r-markdown
documents from plain R codes. The tasks of this package are the automatic
generation of reports from R sessions as well as producing templates that can
be shared as R-functions.

# Installing yamlme

To install this package from its **GitHub** repository, you can use
the package `devtools`.

```{r eval = FALSE}
library(devtools)
install_github("kamapu/yamlme", build_vignettes = TRUE)
```

To start a new session, load the package:

```{r}
library(yamlme)
```

# Writting yaml heads

Several internal funcions and classes are implemented in this package, while
the only visible result will be produced by the function `write_rmd()`.
Each entry in the yaml head can be provided as custom argument in this
function, where at the moment four different categories are defined.

A vector of lentght 1 is the basing entry for a head, for instance:

```{r}
cat(write_rmd(title = "My first document"))
```

Some applications may also require a description (or abstract) as in the case of
documents rendered by `distill`.
To add a description in post you start with a vertical line as first element in
the vector.

```{r}
cat(write_rmd(description = c("|",
						"This text starts with a vertical line",
						"and will be thus used as a description",
						"in the head.")))
```

A similar way is applied in the case of the entries for the element `vignette`
in a vignette document.

```{r}
cat(write_rmd(
				title = "Introduction to this package",
				vignette = c(">",
						paste0("%\\VignetteIndexEntry{", title, "}"),
						"%\\VignetteEngine{knitr::rmarkdown}",
						"%\\VignetteEncoding{UTF-8}")))
```

A further class is used for entries starting with a dash symbol.

```{r}
cat(write_rmd(author=c("- name: Miguel Alvarez",
						"url: https://kamapu.github.io/",
						"- name: Bisrat H. Gebrekhidan")))
```

And finaly, nested entries can be provided as lists.

```{r}
cat(write_rmd(output=list(pdf_document="default")))
```

# A full example

With the function `write_rmd()` you can create a full r-markdown document. You
cam either assign the result to an object or write it in a file, or both.
For it, the parameters `filename` (name and path for the output file), `body`
(body of the document as caracter vector), and `append` (appended blocks in
yaml-head, for instance comments) are suitable.

```{r}
my_document <- write_rmd(title = "Mi First Document", author = "My Name",
		output = "html_document", append = "# This is a comment in head",
		body = txt_body(
				"# Starting a working day",
				"",
				"At the beginning of every day I will do:",
				"",
				"- Say everyone \"Good morning!\"",
				"- Start the coffe mashine",
				"- Start the computer",
				"- Read mails"))
cat(my_document)
```

In this case we can render the document directly from the resulting object.

```{r eval = FALSE}
render_rmd(input = my_document, output_file = "my_document")
```

# Creating a template in a function

A template in `yamlme` can be defined as a function setting default arguments
that will be passed to `write_rmd()`.

```{r}
my_template <- function(
		title = "My Awesome Document",
		author = "My Self",
		output = "html_document",
		body = txt_body(
				"# Introduction",
				"",
				"This is just an example."),
		...) {
	write_rmd(
			title = title,
			author = author,
			output = output,
			body = body,
			...)
}
```

Thus we can just call this function without setting any argument to produce the
template.

```{r}
cat(my_template())
```

We can also modify the template to adapt the output or the template of the
document.

```{r}
cat(my_template(
				output = "pdf_document",
				append = "# this is a modified version"
))
```

Note that the original template will be rendered as a HTML document, while the
second alternative will produce a PDF document.

```{r eval = FALSE}
# Modify only the title of the template and render
render_rmd(my_template(title = "Example HTML document"))

# Modify title and output format before rendering
render_rmd(my_template(title = "Example PDF document", output = "pdf_document"))
```
